Dynamic Anomaly Detection for Collective Data via Statistical Distance

### 2017-10-01 Paper/Template/paper.tex
Modify

% IEEE Paper Template for US-LETTER Page Size (V1)
% Sample Conference Paper using IEEE LaTeX style file for US-LETTER pagesize.
% Copyright (C) 2006-2008 Causal Productions Pty Ltd.
% Permission is granted to distribute and revise this file provided that
% this header remains intact.
%
% REVISION HISTORY
% 20080211 changed some space characters in the title-author block
%
\documentclass[10pt,conference,letterpaper]{IEEEtran}
\usepackage{times,amsmath,amsfonts,epsfig}
\usepackage{graphicx}
\usepackage{algorithm,algorithmicx,algpseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\usepackage{color}
%
\title{Dynamic Anomaly Detection for Collective Data via Statistical Distance}
%
\author{%
	% author names are typeset in 11pt, which is the default size in the author block
	{Ruoyu Wang{\small $~^{\#1}$}, Daniel Sun{\small $~^{*2}$}, Guoqiang Li{\small $~^{\#3}$} }%
	% add some space between author names and affils
	\vspace{1.6mm}\\
	\fontsize{10}{10}\selectfont\itshape
	% 20080211 CAUSAL PRODUCTIONS
	% separate superscript on following line from affiliation using narrow space
	$^{\#}$\,School of Software Engineering, Shanghai Jiao Tong University\\
	No.800 Dongchuan Rd. Shanghai, 200240, China\\
	\fontsize{9}{9}\selectfont\ttfamily\upshape
	%
	% 20080211 CAUSAL PRODUCTIONS
	% in the following email addresses, separate the superscript from the email address 
	% using a narrow space \,
	% the reason is that Acrobat Reader has an option to auto-detect urls and email
	% addresses, and make them 'hot'.  Without a narrow space, the superscript is included
	% in the email address and corrupts it.
	% Also, removed ~ from pre-superscript since it does not seem to serve any purpose
	$^{1}$\,solftwarewry@sjtu.edu.cn\\
	$^{3}$\,li.g@sjtu.edu.cn%
	% add some space between email and affil
	\vspace{1.2mm}\\
	\fontsize{10}{10}\selectfont\rmfamily\itshape
	% 20080211 CAUSAL PRODUCTIONS
	% separated superscript on following line from affiliation using narrow space \,
	$^{*}$\,Data61, Commonwealth Scientific and Industrial Research Organization, Australia\\
	\fontsize{9}{9}\selectfont\ttfamily\upshape
	% 20080211 CAUSAL PRODUCTIONS
	% removed ~ from pre-superscript since it does not seem to serve any purpose
	$^{2}$\,daniel.sun@data61.csiro.au
}

>>>>

% IEEE Paper Template for US-LETTER Page Size (V1)
% Sample Conference Paper using IEEE LaTeX style file for US-LETTER pagesize.
% Copyright (C) 2006-2008 Causal Productions Pty Ltd.
% Permission is granted to distribute and revise this file provided that
% this header remains intact.
%
% REVISION HISTORY
% 20080211 changed some space characters in the title-author block
%
\documentclass[10pt,conference,letterpaper]{IEEEtran}
\usepackage{times,amsmath,amsfonts,epsfig}
\usepackage{graphicx}
\usepackage{algorithm,algorithmicx,algpseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\usepackage{color}
\usepackage{flushend}
%
\title{Dynamic Anomaly Detection for Collective Data via Statistical Distance}
%
\author{%
	% author names are typeset in 11pt, which is the default size in the author block
	{Ruoyu Wang{\small $~^{\#1}$}, Daniel Sun{\small $~^{*2}$}, Guoqiang Li{\small $~^{\#3}$} }%
	% add some space between author names and affils
	\vspace{1.6mm}\\
	\fontsize{10}{10}\selectfont\itshape
	% 20080211 CAUSAL PRODUCTIONS
	% separate superscript on following line from affiliation using narrow space
	$^{\#}$\,School of Software, Shanghai Jiao Tong University\\
	Shanghai, 200240, China\\
	\fontsize{9}{9}\selectfont\ttfamily\upshape
	%
	% 20080211 CAUSAL PRODUCTIONS
	% in the following email addresses, separate the superscript from the email address 
	% using a narrow space \,
	% the reason is that Acrobat Reader has an option to auto-detect urls and email
	% addresses, and make them 'hot'.  Without a narrow space, the superscript is included
	% in the email address and corrupts it.
	% Also, removed ~ from pre-superscript since it does not seem to serve any purpose
	$^{1}$\,trams.wang.ruoyu@gmail.com\\
	$^{3}$\,li.g@sjtu.edu.cn%
	% add some space between email and affil
	\vspace{1.2mm}\\
	\fontsize{10}{10}\selectfont\rmfamily\itshape
	% 20080211 CAUSAL PRODUCTIONS
	% separated superscript on following line from affiliation using narrow space \,
	$^{*}$\,Data61, Commonwealth Scientific and Industrial Research Organization, Australia\\
	\fontsize{9}{9}\selectfont\ttfamily\upshape
	% 20080211 CAUSAL PRODUCTIONS
	% removed ~ from pre-superscript since it does not seem to serve any purpose
	$^{2}$\,daniel.sun@data61.csiro.au
}
